Integer Programming from Quantum Annealing and Open Quantum Systems

### 2020-09-23 paper/main.tex
Fix typo in master eqn

We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
Converting to the Ising representation of the the problem Hamiltonian,
\begin{equation}
    \label{eq:HIsing}
     H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i ,
\end{equation}
we recognize that Eq.~(\ref{eq:HIsing}) exhibits spin-glass properties. More specifically, if the $h_i$ coefficients are randomly drawn from a Bernoulli distribution, one expects spin-localization behavior to influence the outcome of the anneal.
In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001,ALET2018498,PhysRevB.82.174411,PhysRevLett.109.017202}.

@@

The integer linear optimization problem is then solved through the minimization of the quadratic objective function
\begin{align}
 \label{eq:ilp-slack-bit-energy}
 \chi^2(\vec \Psi)
 &=
 \vec c^T T_x \vec \Psi_x + p \left\| A T_s \vec \Psi_x + T_s \vec \Psi_s + \vec b \right\|^2
\end{align}
where $p$ is an external parameter representing the strength of the penalty when violating constraints.
This parameter needs to be sufficiently large, e.g., $p \geq \vec c \cdot \vec x$, to ensure the constraints are indeed fulfilled\footnote{Depending on the problem, $p$ can be smaller as well.
For example, in the case of the MDS, $p\geq 1$ suffices.}.
The objective function $\chi^2$ can be represented as a QUBO Hamiltonian
\begin{align}
 \chi^2(\vec \Psi) =    &
 \vec \Psi^T
 \begin{pmatrix}
  Q_{xx} & Q_{xs} \\
  Q_{sx} & Q_{ss}
 \end{pmatrix}
 \vec \Psi + p\left \| \vec b \right\|^2, \\
 \equiv &  \vec \Psi^T Q  \vec \Psi + C,
 \label{eq:matrix_form}
\end{align}
where
{\small
\begin{align}
 \label{eq:qubo:components}
 Q_{xx} = & p {T_{x}}^T \left[ A^T A + \mathrm{diag} \left(A^T \vec b + \vec b^T A\right) \right] T_x + \mathrm{diag}(\vec c) T_x,                                                                    \\
 Q_{xs} = & Q_{sx}^T = p {T_{x}}^T A^T T_s,                                                                     \\
 Q_{ss} = & p\left[ {T_{s}}^T T_s + \mathrm{diag}\left( {T_{s}}^T \vec b + \vec b^T T_s\right) \right].
\end{align}}
The function $\mathrm{diag}(\vec v)$ transforms a vector $\vec v$ into a diagonal matrix, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.

>>>>

We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delay the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
Converting to the Ising representation of the the problem Hamiltonian,
\begin{equation}
    \label{eq:HIsing}
     H^{\textrm{problem}} \leftrightarrow H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i ,
\end{equation}
we recognize that Eq.~(\ref{eq:HIsing}) exhibits spin-glass properties. More specifically, if the $h_i$ coefficients are randomly drawn from a Bernoulli distribution, one expects spin-localization behavior to influence the outcome of the anneal.
In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001,ALET2018498,PhysRevB.82.174411,PhysRevLett.109.017202}.

@@

The integer linear optimization problem is then solved through the minimization of the quadratic objective function
\begin{align}
 \label{eq:ilp-slack-bit-energy}
 \chi^2(\vec \Psi)
 &=
 \vec c^T T_x \vec \Psi_x + p \left\| A T_x \vec \Psi_x + T_s \vec \Psi_s + \vec b \right\|^2
\end{align}
where $p$ is an external parameter representing the strength of the penalty when violating constraints.
This parameter needs to be sufficiently large, e.g., $p \geq \vec c \cdot \vec x$, to ensure the constraints are indeed fulfilled\footnote{Depending on the problem, $p$ can be smaller as well.
For example, in the case of the MDS, $p\geq 1$ suffices.}.
The objective function $\chi^2$ can be represented as a QUBO Hamiltonian
\begin{align}
 \chi^2(\vec \Psi) =    &
 \vec \Psi^T
 \begin{pmatrix}
  Q_{xx} & Q_{xs} \\
  Q_{sx} & Q_{ss}
 \end{pmatrix}
 \vec \Psi + p\left \| \vec b \right\|^2, \\
 \equiv &  \vec \Psi^T Q  \vec \Psi + C,
 \label{eq:matrix_form}
\end{align}
where
{\small
\begin{align}
 \label{eq:qubo:components}
 Q_{xx} = & p {T_{x}}^T \left[ A^T A + \mathrm{diag} \left(A^T \vec b + \vec b^T A\right) \right] T_x + \mathrm{diag}(\vec c) T_x,                                                                    \\
 Q_{xs} = & Q_{sx}^T = p {T_{x}}^T A^T T_s,                                                                     \\
 Q_{ss} = & p\left[ {T_{s}}^T T_s + \mathrm{diag}\left( {T_{s}}^T \vec b + \vec b^T T_s\right) \right].
\end{align}}
The function $\mathrm{diag}(\vec v)$ transforms a vector $\vec v$ into a diagonal matrix, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.
